Report

### 2021-03-08 Rmd/report.Rmd
First attempt to merge Barcelona and Oxford data (with mild success)

# load functions
source(here("R", "utils.R"))

# load data
stimuli <- readRDS(here("Results", "stimuli.rds"))
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
fit <- readRDS(here("Results", "fit_trials.rds"))
```

@@

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# plot participants
participants %>% 
	drop_na() %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(~age_group) +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

@@

attrition %>% 
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing, participant, colour = valid_trial)) +
	geom_point(alpha = 0.5) +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 9)

@@

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

>>>>

# load functions
source(here("R", "utils-others.R"))
source(here("R", "utils-vocabulary.R"))
source(here("R", "utils-participants.R"))
source(here("R", "utils-gaze.R"))

# load data
stimuli <- readRDS(here("Results", "stimuli.rds"))
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
fit <- readRDS(here("Results", "fit_trials.rds"))

@@

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

@@

attrition %>% 
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing, participant, colour = valid_trial)) +
	geom_point(alpha = 0.5) +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 15)

@@

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(location~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))
